\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Precision Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Fixed Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Standard Subheading command
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Anupal Anil Umale} \\ \vspace{1pt}
    \small +91 7028843375 $|$ \href{mailto:mailanupal@gmail.com}{\underline{mailanupal@gmail.com}} $|$ 
    \href{https://linkedin.com/in/anupal-umale}{\underline{linkedin.com/in/anupal-umale}} $|$
    \href{https://github.com/normiecoder01}{\underline{github.com/normiecoder01}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Impact-driven \textbf{Backend Engineer} specializing in \textbf{Golang} and \textbf{Distributed Systems}. Expert in architecting high-concurrency engines (1M+ records), event-driven systems (Kafka/SQS), and secure microservices. Transitioning from .NET to build production-grade Go software with a focus on observability and performance.}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, nosep]
    \item \small{
     \textbf{Languages}: Go (Golang), SQL (PostgreSQL), TypeScript, C\# (.NET), JavaScript. \\
     \textbf{Backend/Infra}: Microservices, gRPC, Kafka, Redis, Docker, Kubernetes, AWS (S3/SQS), Makefile. \\
     \textbf{Concepts}: Concurrency (Goroutines/Channels), Worker Pools, Clean Architecture, Repository Pattern, DDD. \\
     \textbf{Tools}: Zerolog, Prometheus, Git, pprof, Postman, Jira, OpenSearch.
    }
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
      {Mercedes-Benz (via TEKsystems \& NTT Data)}{Pune, MH}
      {Full Stack Developer}{Feb 2025 -- Present}
      \begin{itemize}[nosep, leftmargin=1.5em]
        \item \small{\textbf{Awarded 'Mobility Maverick'} for end-to-end delivery of a production-grade Chatbot.}
        \item \small{\textbf{Architected} a high-concurrency Go data engine using \textbf{Worker Pools} and \textbf{Goroutines} for \textbf{1M+ records}.}
        \item \small{Developed secure wrapper APIs with \textbf{OAuth 2.0/JWT} and \textbf{Redis} for sub-millisecond responses.}
        \item \small{Optimized distributed architecture using the \textbf{Mediator Pattern} and \textbf{Clean Architecture}.}
        \item \small{Integrated \textbf{structured logging (Zerolog)} and context-timeouts for production observability.}
      \end{itemize}

    \resumeSubheading
      {Thinkbridge Software Pvt. Ltd}{Pune, MH}
      {Software Developer Trainee}{May 2024 -- Oct 2024}
      \begin{itemize}[nosep, leftmargin=1.5em]
        \item \small{Built core business logic in \textbf{Go} using the \textbf{Repository Pattern} with high testability.}
        \item \small{Optimized data flows between Angular and \textbf{Azure Cosmos DB} using DTOs.}
        \item \small{Streamlined workflows by authoring \textbf{Makefiles} and managing \textbf{Docker} containerization.}
      \end{itemize}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item 
    \textbf{\small Concurrent Resource Orchestrator} \hfill \small Go, HTTP/TLS \\
    \begin{itemize}[nosep, leftmargin=1.5em]
      \item \small{Engineered a concurrent engine using \textbf{Goroutines/WaitGroups} for parallel tasks.}
      \item \small{Implemented a \textbf{Semaphore Pattern} via buffered channels to prevent OS socket exhaustion.}
    \end{itemize}
    
    \vspace{2pt}
    
    \item 
    \textbf{\small Event-Driven Commerce Engine} \hfill \small Go, Kafka, DDD \\
    \begin{itemize}[nosep, leftmargin=1.5em]
      \item \small{Architected a dual-interface API using \textbf{Watermill} and \textbf{SQS} to decouple services.}
      \item \small{Implemented secure auth with \textbf{JWT Refresh Token rotation} and \textbf{DDD} principles.}
    \end{itemize}
\end{itemize}

%-----------TECHNICAL STRENGTHS-----------
\section{Technical Strengths}
\begin{itemize}[leftmargin=0.15in, label={}, nosep]
    \item \small{\textbf{System Design}: Proficient in Microservices, Event-Driven Architecture, and API design.}
    \item \small{\textbf{Concurrency}: Deep understanding of Goroutine lifecycles and synchronization.}
    \item \small{\textbf{Reliability}: Focus on Graceful Shutdowns, Structured Logging, and Context-timeouts.}
\end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}, nosep]
    \item \small{\textbf{Technical Consultant}: Automated academic workflows at Rajmata Public School (2020--2024).}
    \item \small{\textbf{National E-Karting}: Competed in National E-Kart Championship (2020).}
    \item \small{\textbf{Certifications}: Joseph Abah's Go Masterclass, PG-Diploma (CDAC ACTS).}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
      {CDAC, ACTS}{Pune, MH}
      {PG-Diploma in Advanced Computing}{Feb 2024}
    \resumeSubheading
      {SGBAU}{Amravati, MH}
      {B.E. in Mechanical Engineering}{May 2020}
\end{itemize}

\end{document}
